---
output: 
  stevetemplates::article2:
    citation_package: natbib
    dev: cairo_pdf
    keep_tex: true
biblio-style: apsr
title: "Title of the semester project"
author:
- name: Student 1
  affiliation: University of Geneva
- name: Student 2
  affiliation: University of Geneva
- name: Student 3
  affiliation: University of Geneva
- name: Student 4
  affiliation: University of Geneva
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
mainfont: cochineal
#sansfont: Linux Biolinum O
fontsize: 11pt
# doublespacing: TRUE
endnote: no
# pandocparas: TRUE
sansitup: FALSE
header-includes:
  - \usepackage{longtable}
  - \LTcapwidth=.95\textwidth
  - \linespread{1.05}
  - \usepackage{hyperref}
---

# Introduction

This is an `R` code chunk

```{r, fig.width=4, fig.height=3}
data=rnorm(100)
plot(density(data), main = "")
```

This is a evaluated but not displayed `R` code chunk

```{r, echo =F, eval =T}
mean_data = mean(data)
```


This is an inline `R` code: Hence, the mean of the data is of `r mean_data`.

This is a $\LaTeX$ equation 

$$
f(x)=\frac{1}{\sigma \sqrt{2 \pi}} \mathrm{e}^{-\frac{1}{2}\left(\frac{x-\mu}{\sigma}\right)^{2}}
$$

# Analysis

# Description of the task

# Motivation

# Results: description and interpretation

# Were these results expected: discussion

# Statistical methods used

# Acquired skills during the term project

# Additionnal element